\section{Introduction}
\label{sec:intro}

% Paragraph 1 — NBA context & multimedia gap
Next Best Action (NBA) systems are decision-support tools used in customer
service and marketing to identify the most appropriate action for each
customer at a specific point in time — such as recommending a product,
sending a personalised offer, or suggesting support.
Current NBA research and deployments rely predominantly on
\emph{structured} transaction data: purchase logs, click histories, and
demographic records~\cite{he2020lightgcn}.
However, customers increasingly generate large volumes of
\emph{unstructured and multimedia} data — natural language queries, images,
and rich interaction sequences — which, if effectively leveraged, can
provide crucial contextual signals for more accurate and personalised
recommendations.
Bridging the gap between structured behavioural signals and unstructured
multimedia content is therefore a central challenge in modern NBA system
design.

% Paragraph 2 — Domain narrowing & interaction-content gap
In the domain of book discovery, this challenge is especially acute.
Users who know what they want issue free-text or image-based queries
(active search), while passive browsers benefit most from proactive
suggestions derived from their interaction history (passive recommendation).
Most existing systems address only one of these modes, leaving an
\emph{interaction-content gap}: behavioural co-purchase signals are
decoupled from semantic content understanding (titles, descriptions, cover
images).
Collaborative filtering excels at crowd wisdom but suffers from cold-start
and ignores multimodal content~\cite{he2020lightgcn}.
Sequential models~\cite{kang2018self} capture preference evolution but
typically discard visual signals.
Content-based encoders retrieve semantically relevant items but lack the
relational structure that behavioural graphs provide.

% Paragraph 3 — Our approach & contributions
We propose a \textbf{Dual-Mode Multimodal NBA Recommendation System} that
mines text, visual, and behavioural multimedia data jointly, addressing
both the active and passive recommendation settings within a single
architecture:
\begin{itemize}
  \item \textbf{Mode~1 (Active Search):} multilingual query-driven
        retrieval (19 languages via NLLB-200) fusing BGE-M3 text embeddings
        and CLIP image embeddings via Reciprocal Rank Fusion (RRF), with
        optional BM25 keyword boosting and multi-layer LRU caching.
  \item \textbf{Mode~2 (Passive Recommendation):} two complementary
        pipelines — (a)~Cleora graph embeddings for behavioural similarity
        (\emph{People Also Buy}), and (b)~DIF-SASRec sequential
        personalisation (\emph{You Might Like}).
  \item A \textbf{shared user profile} continuously updated after every
        interaction, bridging both modes with temporal weighting and
        enabling online adaptation of the sequential model.
\end{itemize}

% Paragraph 4 — Paper structure
The remainder of this paper is organised as follows.
Section~\ref{sec:related} surveys related work on sequential
recommendation, multimodal retrieval, and graph-based collaborative
filtering.
Section~\ref{sec:overview} describes the overall system architecture.
Section~\ref{sec:method} details each component, including the
multilingual normalisation pipeline and the DIF-SASRec model.
Sections~\ref{sec:exp} and~\ref{sec:results} present the experimental
setup and results.
Section~\ref{sec:conclusion} concludes and outlines future directions.
