\section{Related Work}
\label{sec:related}

% MAJOR REVISION: Restructured all subsections to include explicit per-method
% limitations and cross-method comparisons. Added synthesis subsection at end.

% -------------------------------------------------------------------
\subsection{Sequential Recommendation}
% CHANGED: Added cold-start / ID-dependency limitation for SASRec and BERT4Rec;
%          clarified that DIF-SASRec's side information is supplementary, not
%          a replacement for item IDs; added online-adaptation gap.
% -------------------------------------------------------------------
Self-attentive sequential models are the dominant paradigm for modeling
user preference dynamics over interaction histories.
SASRec~\cite{kang2018self} replaces recurrent encoders with causal
self-attention, establishing a strong benchmark for next-item prediction.
BERT4Rec~\cite{sun2019bert4rec} extends this with bidirectional masked
modeling for richer sequence representations.
Both are fundamentally \emph{ID-based}: each item is a learned lookup
embedding, causing retrieval failure for unseen items (the cold-start problem)
and precluding zero-shot generalization without retraining.

DIF-SASRec~\cite{xie2022difsr} partially mitigates this by decoupling item
IDs, attributes, and content into separate attention streams, but auxiliary
features remain \emph{supplementary} to the ID embedding; the model still
requires a training-time identifier for every item.
All three models are trained offline, fail on unseen IDs, and support neither
multilingual queries nor real-time adaptation.

% -------------------------------------------------------------------
\subsection{Dense and Multimodal Retrieval}
% CHANGED: Added stateless / no-personalization limitation for CLIP and BGE-M3;
%          noted English-centric pre-training as a deployment barrier; clarified
%          the gap between dense retrieval and behavioral graph integration.
% -------------------------------------------------------------------
CLIP~\cite{radford2021clip} establishes strong cross-modal alignment via
large-scale paired pre-training, enabling direct image--text comparison in a
shared latent space. Its principal limitation is statelessness: queries are
encoded independently with no user history, and its predominantly English
corpus constrains multilingual deployment.

BGE-M3~\cite{chen2024bgem3} extends dense retrieval to multilingual,
multi-granularity queries, handling both symmetric and asymmetric matching.
Its limitation mirrors CLIP's: purely content-based scoring provides no signal
about co-purchase patterns or behavioral history.
Prior multimodal work combining visual and textual embeddings does not couple
these signals with behavioral graph structure or maintain a persistent user
profile shared across search and recommendation.

% -------------------------------------------------------------------
\subsection{Graph-Based Collaborative Filtering}
% CHANGED: Added catalog-coverage limitation for Cleora (375k / 3.08M);
%          identified query-agnostic behavior as a weakness for active search.
%          Added NGCF, LightGCN, PinSage as representative graph-based methods.
% -------------------------------------------------------------------
Graph-based methods learn from co-purchase or co-interaction edges, evolving
from early factorization to modern graph neural networks (GNNs).
NGCF~\cite{wang2019ngcf} propagates embeddings through a bipartite interaction
graph via multi-hop convolutions, capturing high-order connectivity.
LightGCN~\cite{he2020lightgcn} removes non-linear activations and feature
transformations, showing that linear aggregation achieves superior accuracy
with fewer parameters.
PinSage~\cite{ying2018pinsage} scales GNN recommendation to billion-node
graphs via random-walk sampling, demonstrating industrial viability.
Despite these advances, GNN methods require aggregating over the full
interaction graph, incurring memory and compute costs that grow with catalog
size, and typically mandate GPU resources.

Conventional neural CF requires explicit factorization matrices, precluding
deployment over millions of items without approximations.
Cleora~\cite{cleora2021} avoids these costs via deterministic Markov-chain
propagation, producing stable embeddings without factorization or GPU training.
A significant coverage constraint remains: embeddings require at least one
co-purchase edge, covering 375k of 3.08M catalog items (12.2\%).
Graph methods are also \emph{query-agnostic}: they return the same
neighborhood regardless of the typed query, making them unsuitable as a
standalone active search solution.

% -------------------------------------------------------------------
\subsection{Hybrid Retrieval Systems}
% CHANGED: Replaced vague original paragraph with specific structural limitations
%          of existing hybrid systems (single pipeline, static user state, two-modality cap).
% -------------------------------------------------------------------
Hybrid recommenders that combine behavioral and content signals have been
widely studied, but existing systems share three structural limitations.
First, retrieval is a single pipeline with no separation between user-initiated
search and system-initiated suggestions, a distinction critical for
conversational interfaces.
Second, most systems fuse at most two modalities and assume a static user
representation not updated between requests.
Third, user state is maintained implicitly through training rather than as an
explicitly persisted embedding updated after each interaction.
To our knowledge, no existing system simultaneously supports multilingual and
image-based active search, behavioral-graph and sequential passive
recommendations, and a shared continuously-updated user profile.

% -------------------------------------------------------------------
\subsection{Text Encoders for Item Retrieval and Evaluation Methodology}
% KEPT: Content carried forward from previous version; lightly edited for flow
%       and tightened around the evaluation-bias argument.
% -------------------------------------------------------------------
BLaIR~\cite{hou2024amazon} fine-tunes a RoBERTa-Large backbone on
(review\,text, item) contrastive pairs, yielding item embeddings aligned
with review-style queries of moderate length.
Two limitations arise.
First, the model is English-only and degrades on short keyword queries outside
the review-text distribution.
Second, an \emph{evaluation-bias} problem arises when benchmark clicks are
collected from a system using the same encoder: held-out items are structurally
correlated with that encoder, inflating sampled-evaluation metrics.
We address this in Section~\ref{ssec:encoder} by supplementing sampled
evaluation with live text retrieval quality (genre-precision@10 over 22
labelled queries) where no circular bias applies.

% -------------------------------------------------------------------
\subsection{Summary: Gaps Motivating This Work}
% NEW: Synthesis paragraph connecting surveyed limitations to our contributions.
% -------------------------------------------------------------------
The surveyed literature reveals four recurring gaps.
\textit{(i)~ID-bound sequential models} (SASRec, BERT4Rec, DIF-SASRec) cannot
generalize to unseen items in a long-tail catalog without retraining, imposing
a hard ceiling on cold-start coverage.
\textit{(ii)~Stateless dense retrievers} (CLIP, BGE-M3) return relevant results
but are oblivious to user identity and interaction history.
\textit{(iii)~Behavioral graph methods} (Cleora) capture strong co-purchase
signals but cover only a fraction of the catalog and are insensitive to the
content or language of a typed query.
\textit{(iv)~Existing hybrid systems} collapse user-issued queries and
system suggestions into one pipeline, preventing independent optimization
of each mode.
Our system addresses all four gaps: BGE-M3 content embeddings replace item
IDs for zero-shot catalog coverage; complementary pipelines with RRF fuse
textual, visual, and behavioral signals; a persistent temporally-weighted
user profile bridges both modes; and NLLB-200 routing enables multilingual
deployment.
