\section{Methodology}
\label{sec:method}

\subsection{Mode 1: Active Search}
\label{ssec:active}

Given a user query consisting of text $q_t$ and optionally an image $q_i$,
the system produces a ranked list via:

\paragraph{Multilingual query normalization.}
The system supports queries in 19 languages: Vietnamese, French, German,
Spanish, Chinese, Japanese, Korean, Arabic, Portuguese, Russian, Italian,
Thai, Indonesian, Dutch, Polish, Turkish, Ukrainian, Hindi, and Swedish.
Lingua\footnote{\url{https://github.com/pemistahl/lingua-py}} detects the source language in under 1\,ms.
Non-English queries are translated to English by NLLB-200-Distilled-600M~\cite{costa2022nllb}
using a two-tier strategy: a greedy pass ($\text{num\_beams}=1$, $\sim$16\,ms)
followed by a beam-search fallback ($\text{num\_beams}=4$, $\sim$30\,ms) only
when the greedy output retains untranslated source tokens.
English queries and unsupported languages bypass translation entirely.
All translation results are stored in an in-process LRU cache (capacity 2\,048
entries); repeat queries cost 0\,ms regardless of language.

\paragraph{Encoding.}
Text query: $\mathbf{e}_t = \text{BGE-M3}(q_t) \in \mathbb{R}^{1024}$.
Image query: $\mathbf{e}_i = \text{CLIP}(q_i) \in \mathbb{R}^{512}$.
BGE-M3 inference is wrapped in an LRU cache (capacity 4\,096 entries) keyed
on the translated query string, so repeated or structurally identical queries
skip GPU inference entirely and are served from CPU RAM in under 0.1\,ms.

\paragraph{Retrieval.}
FAISS~\cite{johnson2019faiss} HNSW search retrieves top-$K$ candidates from each index independently,
yielding ranked lists $L_t$ and $L_i$.
A Tantivy BM25 search over tokenized titles and descriptions yields $L_k$.

\paragraph{Fusion.}
Reciprocal Rank Fusion (RRF)~\cite{cormack2009rrf} combines the three lists:
\begin{equation}
  s_{\text{RRF}}(d) = \sum_{r \in \{L_t, L_i, L_k\}}
  \frac{1}{k + \text{rank}_r(d)}, \quad k = 60.
  \label{eq:rrf}
\end{equation}
The top-$N$ items by $s_{\text{RRF}}$ are returned with metadata.

% ---

\subsection{Mode 2: Passive Recommendation}
\label{ssec:passive}

\subsubsection{Pipeline A — Behavioral Similarity (People Also Buy).}
\label{sssec:pipelineA}

\begin{enumerate}
  \item \textbf{Behavioral scouting.} The user's 5 most recent interactions
        seed a multi-query FAISS search in Cleora space, yielding 50 candidates.
  \item \textbf{Content veto.} Each candidate is scored against the user's
        aggregated BGE-M3 and CLIP profile vectors.
        Candidates satisfying
        \begin{equation*}
          \max\!\bigl(
            \cos(\mathbf{e}^{\text{bge}}_c,\,\mathbf{p}^{\text{bge}}),\;
            \cos(\mathbf{e}^{\text{clip}}_c,\,\mathbf{p}^{\text{clip}})
          \bigr) < 0.3
        \end{equation*}
        are discarded.
  \item \textbf{Ranking.} Survivors are ranked by cosine similarity to the
        aggregated profile and the top-$K$ are returned.
\end{enumerate}

\subsubsection{Pipeline B — Sequential Personalization (You Might Like).}
\label{sssec:pipelineB}

\begin{enumerate}
  \item \textbf{Candidate generation.} HNSW search on BGE-M3 embeddings of
        the user's recent items retrieves 200 candidates.
  \item \textbf{Content veto.} Same threshold as Pipeline A.
  \item \textbf{Sequential scoring.} DIF-SASRec scores each candidate as the
        predicted next item.
\end{enumerate}

% ---

\subsection{DIF-SASRec Model}
\label{ssec:difsasrec}

We adapt DIF-SASRec~\cite{xie2022difsr} to operate in a content-ID-free setting.
Each item is represented by its BGE-M3 embedding projected to 512 dimensions,
eliminating ID lookup tables.

\paragraph{Architecture.}
The model consists of:
(i)~a linear content projection $\mathbf{W}_c \in \mathbb{R}^{1024 \times 512}$,
(ii)~4 transformer blocks with causal self-attention,
(iii)~a dual-stream attention mechanism with separate Q/K heads for content
and category, fused by a learnable scalar $\alpha$, and
(iv)~a dot-product prediction head.
Total parameters: 12.4M.

\paragraph{Training.}
We train on 100k users from Amazon Books with an 80/20 temporal split.
Sampled softmax loss with 512 negatives per step scales to the 3M-item catalog.
An auxiliary category classification loss with weight $\lambda = 0.1$
stabilizes genre-level understanding.
We use AdamW~\cite{loshchilov2019decoupled} ($\text{lr}=10^{-3}$, $\text{wd}=0.01$) with linear warmup
(2 epochs) and cosine decay over 30 epochs, batch size 2048 with AMP float16.

\paragraph{Online adaptation.}
At inference, each user's agent fine-tunes on a single interaction step via
back-propagation before each recommendation, enabling real-time personalization
without retraining the full model.
An \textbf{AgentPool} of 8 independent model instances handles concurrent
requests safely, each holding a pretrained weight snapshot in CPU RAM for
cold-start initialization.
