\section{Experiments and Results}
\label{sec:exp}
\label{sec:results}

\paragraph{Dataset.}
We use the Amazon Reviews 2023 Books subset~\cite{hou2024amazon}, a large-scale
e-commerce benchmark pairing user reviews with item metadata.
The raw corpus contains 29,475,453 review records and 4,448,181 item metadata
records (Table~\ref{tab:dataset}).
We retain users with at least 5 interactions, yielding 100,000 users over a
3.08M-item catalog; 375,000 items (12.2\%) carry at least one co-purchase edge
and are covered by the behavioral graph embedding, with an average interaction
sequence of 33.5 clicks per user.

\input{tables/dataset_stats}

Three distributional properties of the dataset directly inform system design.
First, item cover images are available for 99.1\% of catalog entries while
user-uploaded review images appear in only 1.8\% of reviews, motivating
item-side visual embeddings rather than review-image features.
Second, approximately 80\% of reviews carry a rating of 4 or 5 stars,
following the J-shaped positive bias common in e-commerce~\cite{hou2024amazon};
this skew precludes ratings as a primary relevance signal and motivates
content-based evaluation.
Third, review text exhibits a right-skewed length distribution (median 37 words,
mean 86 words), confirming that most sequences fit within standard transformer
token budgets without aggressive truncation.

The last interaction of each user is held out as the test item; the remaining
history forms the training sequence.

\paragraph{Evaluation Metrics.}
We report HR@10 and NDCG@10.
Following the protocol of SASRec~\cite{kang2018self} and
DIF-SASRec~\cite{xie2022difsr}, each held-out item is ranked against 99 random
negatives (random-chance HR@10 = 0.10).
We also evaluate under a 999-negative protocol (random-chance HR@10 = 0.01)
to assess robustness (Section~\ref{ssec:robustness}).

\paragraph{Baselines.}
\input{tables/baselines}

% \paragraph{Implementation Details.}
% All experiments run on a single RTX~5060~Ti (16\,GB).
% DIF-SASRec uses AdamW ($\text{lr}=10^{-3}$, wd~$0.01$), linear warmup
% (2 epochs), cosine decay to $10^{-5}$ over 30 epochs, batch 2\,048, AMP
% float16, 512 sampled softmax negatives, and $\lambda = 0.1$ for the category
% loss.
% FAISS HNSW uses $M=32$, $\text{ef\_construction}=200$, $\text{ef\_search}=128$.
% Cleora uses 3 Markov propagation steps; BGE-M3 and CLIP run in FP16 on GPU;
% BM25 on CPU. The AgentPool holds 8 DIF-SASRec instances (148\,MB each,
% 1.18\,GB total).
