\section{Results}
\label{sec:results}

\subsection{Recommendation Performance}
Table~\ref{tab:main_results} reports HR@10 and NDCG@10 under the
sampled evaluation protocol (99 random negatives, random tiebreak).

\input{tables/main_results}

\paragraph{Pipeline~A (Cleora + BGE-M3).}
Pipeline~A achieves the highest standalone HR@10 of \textbf{0.7626}
(NDCG@10 = 0.4867), a $+75.2\%$ improvement over the Content-KNN
baseline (0.4353).
By restricting the candidate space to items within the Cleora behavioral
co-purchase graph and ranking by BGE-M3 profile similarity, Pipeline~A
leverages both behavioral and semantic signals simultaneously.

\paragraph{DIF-SASRec (Pipeline~B).}
DIF-SASRec achieves HR@10 = 0.4836 (NDCG@10 = 0.3737), an $+11.1\%$
improvement over Content-KNN (0.4353), confirming that sequential
modeling captures preference dynamics that nearest-neighbor retrieval
misses.

\paragraph{Dual-pipeline system.}
The union of Pipeline~A and Pipeline~B top-10 lists achieves
\textbf{HR@10 = 0.7886} (NDCG@10 = 0.5409), the best overall result.
Table~\ref{tab:complementarity} breaks down the per-user hit patterns.
Pipeline~A rescues \textbf{59.0\%} of DIF-SASRec misses, while
DIF-SASRec rescues \textbf{11.0\%} of Pipeline~A misses.
The two pipelines serve genuinely different user--item patterns:
Pipeline~A excels on items with strong behavioral co-purchase signals
(within the Cleora 375k index), while DIF-SASRec provides complementary
sequential intent modeling for items Pipeline~A cannot reach.

\input{tables/complementarity}

\subsection{Robustness Under Stricter Evaluation}
\label{ssec:robustness}

Table~\ref{tab:robustness} repeats the comparison under a 999-negative
protocol (1\,000 candidates; random-chance baseline HR@10 = 0.01),
ten times harder than the standard setting.

\input{tables/robustness_results}

Pipeline~A achieves the highest HR@10 of \textbf{0.3264} at this harder
setting, while DIF-SASRec leads on NDCG@10 (\textbf{0.2209} vs 0.2096),
indicating that DIF-SASRec tends to rank hits closer to position~1
when it does retrieve the target.
Content-KNN drops to 0.2122 HR@10.
Crucially, both Pipeline~A and DIF-SASRec show an \emph{increasing}
relative advantage over the random baseline as the pool grows:
Pipeline~A rises from $7.6\times$ (99-negative) to $32.6\times$
(999-negative); DIF-SASRec from $4.8\times$ to $31.4\times$.
Neither model's performance is an artefact of easy negatives in the
standard pool.

\subsection{Ablation Study}
Table~\ref{tab:ablation} reports both pipeline-level and component-level
ablations.

\input{tables/ablation}

\paragraph{Pipeline ablation.}
Pipeline~A alone (+57.6\% over Pipeline~B baseline) demonstrates that
behavioral co-purchase structure combined with BGE-M3 profile similarity
is a powerful retrieval signal in the books domain.
The full union system adds a further +3.4\% relative by incorporating
DIF-SASRec's complementary sequential modeling for items outside
Cleora's behavioral coverage.

\paragraph{Category auxiliary loss.}
Removing the auxiliary category classification head reduces DIF-SASRec
HR@10 by $1.8\%$, indicating that genre-level supervision provides a
useful inductive bias for distinguishing within-sequence preference drift.

\paragraph{Content veto.}
Disabling the cosine-similarity veto ($\tau=0.3$) in Pipeline~B reduces
HR@10 by $2.1\%$.
Without the veto, DIF-SASRec scores candidates that are semantically
unrelated to the user's latent interests, diluting recommendation precision.

\paragraph{Online adaptation.}
The largest single drop ($-7.9\%$ HR@10) comes from removing the
per-user fine-tuning step.
This confirms that the pretrained model alone under-fits individual
preference trajectories; the online gradient step is the primary driver
of personalization beyond the pretrained prior.

\paragraph{Dual-stream attention.}
Replacing the decoupled content/category attention with a single merged
stream reduces HR@10 by $4.6\%$, validating that keeping textual and
categorical signals in separate attention heads prevents one modality
from dominating the other.

\subsection{Latency Analysis}
Table~\ref{tab:latency} reports the end-to-end latency breakdown measured
under two conditions on an NVIDIA RTX~5060~Ti: (i)~\emph{cold}, using 35
unique queries each executed exactly once so every observation is a
guaranteed LRU and FAISS page-cache miss, and (ii)~\emph{warm}, using
repeated queries after the server has been running long enough for the
HNSW index to be resident in OS page cache and the LRU caches to be
populated.

\input{tables/latency}

\paragraph{Cold path.}
On a unique query with no prior caching, P50 end-to-end latency is
\textbf{1\,127\,ms} for English and 1\,281\,ms for non-English input.
The dominant component is FAISS HNSW text search (P50~906\,ms), which
incurs OS page faults on the 12.6\,GB BGE-M3 HNSW index when graph nodes
are not resident in RAM.
BGE-M3 encoding contributes 40\,ms P50; NLLB translation adds 156\,ms
P50 only for non-English queries.
The flat-index baseline (4\,200\,ms) used prior to HNSW migration is still
$3.7\times$ slower than the cold HNSW path, confirming that HNSW delivers
a meaningful speedup independent of caching.

\paragraph{Warm path.}
Once the HNSW index is paged into OS RAM and LRU caches are populated,
P50 drops to \textbf{17\,ms} (internal) / \textbf{34\,ms} (E2E wall
clock) for English queries.
FAISS search falls to 2\,ms and both translation and encoding are served
from in-process LRU caches at under 1\,ms, so latency is bounded by
Tantivy BM25 ($\sim$6\,ms) and network/serialization overhead.

\paragraph{Production characterisation.}
In a deployed system, the server issues a warmup routine at startup
(pre-querying representative terms to page the HNSW index into RAM)
before accepting live traffic.
After warmup, unique new queries incur only the BGE-M3 encoding cost
($\sim$40\,ms P50) plus fast FAISS search ($\sim$2\,ms) once the index
is resident, yielding a realistic steady-state P50 of approximately
60--80\,ms for English queries.
Repeated or popular queries are served entirely from LRU caches at
$<$25\,ms P50.

\subsection{Concurrency and Memory}
The AgentPool of 8 independent DIF-SASRec instances sustains throughput
for 10+ simultaneous users with no observed weight corruption, validated
by stress-testing with 20 concurrent requests.
Each agent holds a pretrained weight snapshot in CPU RAM ($\sim$148\,MB)
for new-user cold-start initialization, with fine-tuned weights kept in
GPU memory only for the duration of the request.
Total pool VRAM footprint is 1.18\,GB, leaving headroom on the 16\,GB card
for the FAISS HNSW indices and encoder models.

\subsection{Encoder Comparison: BLaIR vs.\ BGE-M3}
\label{ssec:encoder}

Table~\ref{tab:encoder_comparison} compares the legacy BLaIR
encoder~\cite{hou2024amazon} against the production BGE-M3
encoder~\cite{chen2024bgem3} along two axes.

\paragraph{Item-similarity sampled evaluation.}
Under the standard 99-negative protocol, BLaIR outperforms BGE-M3 on all
ranking metrics (HR@10: 0.5484 vs.\ 0.4510, NDCG@10: 0.3513 vs.\ 0.3128).
This result must be interpreted in light of the evaluation bias discussed in
Section~\ref{sec:related}: the benchmark set was collected while BLaIR was
the live system, so held-out clicks are structurally correlated with
BLaIR's embedding space.
Score distribution analysis confirms the artefact: BLaIR's intra-genre
cosine similarity (0.819) and inter-genre cosine similarity (0.765) are
nearly indistinguishable — a separation ratio of only 1.071 — indicating
embedding collapse rather than discriminative semantic structure.
BGE-M3 achieves a higher separation ratio (1.181), reflecting a
well-distributed embedding space where genre clusters are more distinct.

\paragraph{Text query retrieval quality.}
Loading both encoders live and issuing 22 labelled text queries against
their respective HNSW indices reveals the operational reality.
BGE-M3 leads on every group except single-token English queries: medium
(genre-precision@10 0.333 vs.\ 0.083), long (0.400 vs.\ 0.200), and all
Vietnamese groups (0.275--0.550 vs.\ 0.025--0.050).
On short single-token queries (e.g., ``mystery'', ``horror''), BLaIR
marginally outperforms BGE-M3 (0.233 vs.\ 0.150); we attribute this to
BLaIR's collapsed similarities incidentally returning genre-coherent
neighborhoods regardless of the query token.
For Vietnamese, BLaIR returns near-random results in both the short and
long groups — a structural limitation of its English-only training — while
BGE-M3's multilingual pre-training yields genre-precision of 0.275 and
0.550 respectively.
Since our system's primary interaction mode is typed text search (including
Vietnamese), and since BLaIR's sampled-evaluation advantage is confounded
by evaluation bias, we select BGE-M3 as the production encoder.

\input{tables/encoder_comparison}
